Gov 50 Final Project

### 2022-10-20 article.Rmd
hh

---
title: "Gov 50 Final Project"
author: "Mashal Farrukh"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
library(distill)
create_article("article.Rmd")
```

## Project thoughts

@@

I am also interested in exploring data related to the Covid 19 Pandemic and the how that has impacted Gender equity, especially domestic violence against women in different countries.

>>>>

---
title: "Gov 50 Final Project"
description: |

@@

I am also interested in exploring data related to the Covid 19 Pandemic and the how that has impacted Gender equity, especially domestic violence against women in different countries. 
author:
  - name: Mashal Farrukh 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
